Making Sequential Programs Deterministic

### 2019-04-06 design.tex
sec 2 edits

\paragraph{Discussion of the type of \<length>}

@@

A similar typing does \emph{not} work for the \<set> function that sets an
element of a list.  Consider the putative type

@@

More specifically, rule \rulename{set precision} of
\cref{fig-precision-rules} expresses that the return type of \<equals()>
is \<Det> if both arguments have type \<OrderNonDet Set> and nether argument
has {@code List} or a subtype within its type argument.
Without this rule, the type would be \<NonDet> which is sound but imprecise.

>>>>

\paragraph{Discussion of the type of \<first>}

@@

A similar typing does \emph{not} work for the \<set> function that sets an
element of a list.  Consider the mutative type

@@

More specifically, rule \rulename{set precision} of
\cref{fig-precision-rules} expresses that the return type of \<equals()>
is \<Det> if both arguments have type \<OrderNonDet Set> and neither argument
has {@code List} or a subtype within its type argument.
Without this rule, the type would be \<NonDet> which is sound but imprecise.
